To Do

### 2019-01-24 To_Do.Rmd
trends compiled

[ ] Bartomeus PNAS estimates (Nacho) 
[X] Scheper PNAS estimates (MA)
[X] UE red list (via @ropensci; MA)
[X] SPAIN trends (MA: species with Brain size) 
[ ] Trends: Nacho or Cristina

>>>>

[X] Bartomeus PNAS estimates (Nacho) 
[X] Scheper PNAS estimates (MA)
[X] UE red list (via @ropensci; MA)
[X] SPAIN trends (MA: species with Brain size) 
[ ] Trends: Nacho or Cristina
